---
title: "p8105_hw1_ww2744"
author: "Wenjie Wu"
date: "2024-09-16"
output: html_document
---

```{r setup, echo = FALSE, message = FALSE}
library(palmerpenguins)
library(ggplot2)
library(tidyverse)
```

# Problem 1

## Import penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
```

## Penguins dataset Description

The `penguins` dataset  contains 344 rows and 8 cols

- `species`: The species of the penguins (Adelie, Chinstrap, Gentoo).
- `island`: The island where the penguins were found.
- `bill_length_mm`: The length of the penguins' bills in millimeters.
- `bill_depth_mm`: The depth of the penguins' bills in millimeters.
- `flipper_length_mm`: The length of the penguins' flippers in millimeters.
- `body_mass_g`: The penguins' body mass in grams.
- `sex`: The sex of the penguin (male, female).
- `year`: The year of birth of the penguin (2007, 2008, 2009).

The mean flipper length is `r round(mean(dplyr::pull(penguins, flipper_length_mm), na.rm = TRUE))`mm.


# Create the scatterplot

```{r, message = FALSE, warning = FALSE}
ggplot(
  data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(
    title = "Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Penguin Species"
  ) +
  theme_minimal()

ggsave("scatterplot_flipper_vs_bill.png")

```


# Problem 2

## Create Dataframe

```{r}
df = 
  tibble(
  norm_sample = rnorm(10),
  samp_g0 = norm_sample > 0,
  char_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vector = factor(c("Low", "Mid", "High", "Low", "Mid", "High", "Low", "Mid", "High", "Low"))
)
```

## Mean

```{r, warning = FALSE}
dbl_mean = mean(pull(df, norm_sample)) |>
  print()
lgl_mean = mean(pull(df, samp_g0)) |>
  print()
chr_mean = mean(pull(df, char_vector)) |>
  print()
fct_mean = mean(pull, factor_vector) |>
  print()
```

Double and Logical vector works

Character and Factor vector does not work

```{r, warning = FALSE}
lgl_num = as.numeric(pull(df, samp_g0))
chr_num = as.numeric(pull(df, char_vector))
fct_num = as.numeric(pull(df, factor_vector))
```

Logical vector: `True` values are converted to 1 and `False` values are converted to 0

Character vector: Return `NA` and issue a warning

Factor vector: Stored internally as integers corresponding to the level order.

